---
title: 'Course Project: A Study on the Effect of Transmission Type on Gas Mileage'
author: "Ryan Hammer"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "hold")
```

## Executive Summary

The purpose of this analysis was to determine whether the type of transmission in an automobile (automatic or manual) has a measurable effect on gas mileage. The data used came from the **mtcars** data set in R, which was extracted from a 1974 issue of _Motor Trend_ magazine and contained data on 32 automobiles. There were 11 different variables included in the data; the focus in the analysis was on the following variables: mpg (Miles/US gallon) and am (transmission type, where 0 = automatic and 1 = manual); however other variables were considered as possible confounders, including: cyl (number of engine cylinders), hp (gross horsepower), (wt, in 1000 lbs), and vs (engine shape where 0 = V-shaped and 1 = straight).
The analysis revealed

## Introduction to Data




It usually contains a brief statement of the problem or proposal covered in the major document(s), background information, concise analysis and main conclusions. It is intended as an aid to decision-making by managers 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
